Model Finding for Recursive Functions in SMT

### 2016-01-28 ijcar2016/body.tex
Cartesian everywhere

The intuition of the above proof is as follows.
First, $\conv( \varphi )$ cannot be unsatisfiable when $\varphi$ is satisfiable
since any $\Sigma$-interpretation that satisfies $\varphi$ can be extended in a straightforward way to
an $\extendsig{\Sigma}$-interpretation that satisfies $\conv( \varphi )$, by
interpreting the abstract types in the same way as the cartesian products they
abstract, thereby satisfying all existential constraints introduced by $\conv$.
Conversely, if a model is found for $\conv( \varphi )$,
existential constraints
%the constraints $\exists a : \fargtype{\con{f}}.\;\, \vecfarg{\con{f}}( a ) \teq \vec t$
introduced by $\conv$ ensure that this model also satisfies
a $\Sigma$-formula that is closed under function expansion and
that entails the goal of $\varphi$.
This implies the existence of a model for $\varphi$
provided that $\DDD$ is admissible.
%For clarity, we demonstrate the consequences of this theorem by means of an example.

>>>>

The intuition of the above proof is as follows.
First, $\conv( \varphi )$ cannot be unsatisfiable when $\varphi$ is satisfiable
since any $\Sigma$-interpretation that satisfies $\varphi$ can be extended in a straightforward way to
an $\extendsig{\Sigma}$-interpretation that satisfies $\conv( \varphi )$, by
interpreting the abstract types in the same way as the Cartesian products they
abstract, thereby satisfying all existential constraints introduced by $\conv$.
Conversely, if a model is found for $\conv( \varphi )$,
existential constraints
%the constraints $\exists a : \fargtype{\con{f}}.\;\, \vecfarg{\con{f}}( a ) \teq \vec t$
introduced by $\conv$ ensure that this model also satisfies
a $\Sigma$-formula that is closed under function expansion and
that entails the goal of $\varphi$.
This implies the existence of a model for $\varphi$
provided that $\DDD$ is admissible.
%For clarity, we demonstrate the consequences of this theorem by means of an example.
